The eclipse of the V773 Tau B circumbinary disk

### 2022-08-10 src/tex/ms.tex
added proof corrections

%\documentclass[referee]{aa} % for a referee version
%\documentclass[onecolumn]{aa} % for a paper on 1 column  
\documentclass{aa}  
\bibliographystyle{aa}

@@

\newcommand{\rsun}{$R_{\odot}$}
\newcommand{\teff}{$T_{\rm eff}$}
\newcommand{\logg}{\ensuremath{\log g}}
\newcommand{\Msun}{$M_{\odot}$}
\newcommand{\logl}{log($L/L_{\odot}$)}
\def\th{\thinspace}
\def\kms{\ifmmode{\rm km\th s^{-1}}\else km\th s$^{-1}$\fi}

@@

\title{The eclipse of the V773 Tau B circumbinary disk\thanks{The manuscript and processing scripts are available in a GitHub repository at \url{https://github.com/mkenworthy/V773TauBdisk}. Processed photometric data and light curves are available in electronic form at the CDS via anonymous ftp to \url{cdsarc.u-strasbg.fr} (130.79.128.5) or via \url{http://cdsweb.u-strasbg.fr/cgi-bin/qcat?J/A+A/}}}

@@

  \abstract
  % context heading (optional)
  % {} leave it empty if necessary  
   {Young multiple stellar systems can host both circumstellar and circumbinary disks composed of gas and dust, and the orientations of circumbinary disks can be sculpted by the orientation and eccentricity of the central binaries.
   %
   Studying multiple binary systems and their associated disks enables understanding of the size and distribution of the planetary systems that subsequently form around them.}
  % aims heading (mandatory)
   {A deep ($\sim 70$\%) and extended ($\sim$150 days) eclipse was seen towards the young multiple stellar system V773 Tau in 2010.
   %
   We interpret it as due to the passage of a circumbinary disk around the B components moving in front of the A components.
   %
 Our aim is to characterise the orientation and structure of the disk, to refine the orbits of the subcomponents, and to predict when the next eclipse will occur.}
  % methods heading (mandatory)
   {We combine the photometry from several ground based surveys, construct a model for the light curve of the eclipse, and use high angular resolution imaging to refine the orbits of the three components of the system, A, B and C.
   %
   Frequency analysis of the light curves, including from the TESS satellite, enables characterisation of the rotational periods of the Aa and Ab stars.}
  % results heading (mandatory)
   {A toy model of the circumbinary disk shows that it extends out to approximately 5 au around the B binary and has an inclination of 73\degr{} with respect to the orbital plane of AB, where the lower bound of the radius of the disk is constrained by the geometry of the AB orbit and the upper bound is set by the stability of the disk.
   %
   We identify several frequencies in the photometric data that we attribute to rotational modulation of the Aa and Ab stellar companions.
   %
   We produce the first determination of the orbit of the more distant C component around the AB system and limit its inclination to 93\degr{}.
   %
}
  % conclusions heading (optional), leave it empty if necessary 
   {The high inclination and large diameter of the disk, together with the match from theory suggest that B is an almost equal mass, moderately eccentric binary.
   %
   We identify the rotational periods of the Aa and Ab stars, identify a third frequency in the light curve that we attribute to the orbital period of the stars in the B binary.
   %
   We predict that the next eclipse will be around 2037, during which both detailed photometric and spectroscopic monitoring will characterise the disk in greater detail.}

@@

Young multiple stellar systems are common \citep[e.g.][]{Ghez93,Duchene13} as are gas disks in and around the stellar components \citep{Akeson19}.
%
Chaotic accretion can occur during the star formation process as a result of turbulence within the molecular cloud from which the stars form \citep{Bate2003,McKee2007}.
%
Circumstellar and circumbinary disks can form with a misalignment to the binary orbital plane \citep{Monin2007, Bate2018}.

These binaries have been shown to influence and sculpt the circumbinary disks around them, possibly reinvigorating planet formation \citep{Cabrit06,Rodriguez18}.
%
%
The torque from a binary or multiple stellar system affects the formation and evolution of gas disks \citep[e.g.][]{Nelson2000, Mayer2005,Boss2006, Fu2017} and the interaction of planets with the disk \citep{Picogna2015,Lubow2016,Martin2016}.
%
Thus understanding how stellar multiplicity affects the formation and evolution of disks is important to explain observed exoplanet properties.

A misaligned circumbinary disk undergoes retrograde nodal precession.
%
If the binary is in a circular orbit, the precession is always around the binary angular momentum vector \citep[e.g.][]{Larwood1996}.
%
However, around an eccentric binary the precession is around the binary eccentricity vector if the initial misalignment is sufficiently high \citep{Farago2010,Aly2015}.
%
Dissipation within the disk causes the disk to align towards coplanar to the binary orbit, or polar to the binary orbit and aligned to the binary eccentricity vector \citep{Martin17,Lubow2018,Zanazzi2018}.
%
While all currently detected circumbinary planets are in coplanar orbits, around an eccentric binary polar planets may be more stable than coplanar planets \citep{Chen2020} and terrestrial planets at least form more efficiently \citep{Childs2021}.
%
If the disk lifetime is shorter than the disk alignment timescale then planets may form in misaligned orbits.

There are now many observations of circumbinary disks with a range of misalignment angles.
%
For example, KH~15D has a misalignment of about $3-15^\circ$ \citep{Chiang2004, Winn2004,Capelo2012,Poon2021}.
%
IRS~43 is misaligned by greater than $60^\circ$ \citep{Brinch16}, and the circumbinary disk around 99 Her has a polar misalignment \citep{Kennedy12}.
%
HD~98800 has a misalignment of $90^\circ$, meaning it is polar aligned to the central binary orbit \citep{Kennedy19,Zuniga-Fernandez21}.
%
Of the two possible disk inclinations allowed by observations, the polar alignment was first suggested by considering the dynamics of a disk since the polar alignment timescale is short compared to the stellar age.
%
Furthermore, the size of the inner hole in the disk that is carved by the binary orbit \citep{Artymowicz1994} is in agreement with a polar alignment \citep{Franchini19}.
%
There is also an external binary companion to the circumbinary disk in this system and its orbit is close to $34^\circ$ to the disk angular momentum.

V773 Tau is a young multiple stellar system that has been intensively studied as described in Section~\ref{sec:v773}.
%
It contains three components, each at a distinctly different stage of young stellar evolution - the A component is an almost equal mass binary, which in itself orbits around an almost equal mass B component that has an edge-on disk around it, forming a hierarchical multiple system with a decades long orbit.
%
Both these components are orbited by a third, C component that is highly embedded within a cloud of dust and is on a several hundred year orbit around both A and B.
%

In Section~\ref{sec:data} we present the photometry of the V773 system from several ground based surveys.
%
A deep extended eclipse occurs over a 200 day period, and we attribute this to a disk around the B component passing in front of the A components.
%
This disk is highly inclined with respect to the AB orbital plane, which should otherwise become coplanar within a dynamically short timescale.
%
Previous work \citep{Boden12} indicates that the B component is itself a tight, almost equal mass binary system.
%
If the B binary is also eccentric, then the disk will experience a torque that keeps it at the inclination that we observe.
%
Time series analysis of the photometry reveals two rotational periods consistent with the stars in the A binary, and a third period of approximately 67 days is revealed in the analysis.
%
If this period is attributed to the orbital period of the B binary, then we show that a moderate orbital eccentricity will keep the circumbinary disk at the observed inclination.
%
We derive the properties of the B binary and the circumbinary disk, and in Section~\ref{sec:orbitalfit} use the astrometry from the direct imaging observations to determine the expected epoch of the next eclipse of the A system.

Section~\ref{sec:variability} details our analysis of the photometric fluctuations due to both rotational modulation of Aa and Ab, and identifies a photometric signal whose period is a plausible measure of the orbit of the BaBb binary.
%
The long and extended eclipse is modeled in Section~\ref{sec:model} as an azimuthally symmetric dusty disk that is highly inclined to the AB orbital plane.
%
Theoretical consideration of the torques from an eccentric binary on a surrounding disk are discussed in Section~\ref{sec:theory} along with the prediction for the timing of the next eclipse in Section~\ref{sec:discuss}.
%
We summarise our results and discuss future observations in Section~\ref{sec:conclusions}.

@@

\begin{figure}
\begin{center}
    \centering
    \includegraphics[width=\columnwidth]{figures/v773_system_cartoon.pdf}
    \caption{Sketch of the V773 Tau system. 
    %
    We hypothesise that B is itself an equal mass binary system with a moderately eccentric orbit.
    %
    Orbits are not to scale.}
\label{fig:cartoon}
\end{center}
\end{figure}

\begin{figure*}
\begin{center}
    \centering
%    \includegraphics[width=\textwidth]{figures/v773tau_fig1.pdf}
    \includegraphics[width=\textwidth]{figures/fig2_full_lightcurve.pdf}
    \caption{Optical photometry of the V773 Tau system.
    %
    The four different photometric surveys are represented by different colours, and each photometric series has been normalised using flux outside the main eclipse.
    %
    The inset panel shows the eclipse light curve in greater detail.
    %
    The PTF and KELT curves show different depths of the eclipse, indicating the presence of sub-micron dust that causes different amounts of optical extinction in the different pass bands of the two surveys.}
  \label{fig:lc}
  \script{fig2_complete_lightcurve.py}
\end{center}
\end{figure*}

@@

V773 Tau (HD 283447, HBC 367) is a young \citep[$3\pm1$ Myr;][]{Boden07} stellar system that was identified as a young T Tauri star \citep{Rydgren76} and subsequently resolved as a visual double \citep{Ghez93,Leinert93}.
%
Its age was determined by comparing the temperature and luminosity of the stars Aa and Ab with PMS stellar models from \citet{Montalban06}, which show excellent consistency with the component parameters from \citet{Boden07}.
%
It is located at a distance of $132.8\pm 2.3 $ pc as determined by orbital and trigonometric parallax \citep{Torres12}, in contradiction with the larger distance determined by Gaia EDR3.
%
We attribute this discrepancy to the multiple source nature of the system which is not resolved by GAIA, and we use the distance determined by the spatially resolved A components with the VLA observations \citep{Torres12}.

The bound components of V773 Tau were initially identified as A, B and C (see Figure~\ref{fig:cartoon}).
%
The A component was resolved by Very Long Baseline Array observations to be a binary system with $P_{AaAb}=51.1003\pm 0.0022$ days and an eccentricity of $e=0.2710\pm 0.0072$ \citep{Torres12}.
%
The A binary becomes more luminous in radio waves during the periastron passage of the A stars, which is thought to be from the interacting magnetic fields of the two stars \citep{Torres12}.

A is orbited by the B component on a period of approximately 26 years, and both A and B are orbited by a C component with an orbital period of several hundred years \citep{Duchene03}.
%
C is a heavily reddened companion that is the faintest component at a wavelength of two microns but is the brightest at $4.7\mu m$ \citep{Duchene03,Woitas03}.
%
The flux contribution from C at optical wavelengths is approximately 100 times fainter than the A and B components \citep{Duchene03}.

@@

Photometry of the B component shows a significantly greater amount of extinction compared to the A component, implying the presence of additional dust along the line of sight to the B component \citep{Torres12}.
%
The B component shows significant photometric variability on the order of 2 to 3 magnitudes in the $K$ band \citep{Boden12}, consistent with clouds or clumps of dust orbiting around the B component.
%
The initial fit to the spectral energy distribution (SED) suggested that the B component consisted of a single K star \citep{Duchene03}, but subsequent radial velocity monitoring and astrometry of the A binary enabled a dynamical mass determination of both the B and A components, revealing a much larger mass of $2.35 M_\odot$ for the B component \citep{Boden12}.
%
A single $2.35 M_\odot$ star would have a luminosity of $17 L_\odot$, inconsistent with the optical luminosity observed and the extinction derived.
%
If the B system is itself a binary, BaBb, then assuming equal mass components of $1.5 M_\odot$ yields a much lower luminosity that is consistent with the observed SED.
%
We therefore assume that the V773 Tau AB system is a hierarchical quadruple system, with a circumbinary disk around the B component which responsible for the significant reddening and photometric variability seen towards the B component.

@@

% table
\begin{table*}
\caption{Orbital parameters for A and B systems. Data from \citet{Torres12} ``Joint solution'' for AaAb and from \citet{Boden12} for A-B. NOTE $\omega_A$ is defined in the RV sense for Torres and Boden, so that you will need to add 180\degr{} to $\omega_A$ for the Torres and Boden orbits to be correctly calculated in orbitize!}              % title of Table
\label{tab:orbs}      % is used to refer this table in the text
\centering                                      % used for centering table
\begin{tabular}{l c c c c}          % centered columns (4 columns)
\hline\hline                        % inserts double horizontal lines
Orbital  & Torres 2012  & Boden 2012    & this work   &  this work \\
 Parameter & AaAb  & AB    & AB   & AB-C  \\

@@

\begin{table}
\caption{Physical parameters for V773 Tau A-B. Data from \citet{Torres12} ``Joint solution'' for AaAb and from \citet{Boden12} for A-B}              % title of Table
\label{tab:physparams}      % is used to refer this table in the text
\centering                                      % used for centering table
\begin{tabular}{l c c}          % centered columns (4 columns)
\hline\hline                        % inserts double horizontal lines
Parameter & Value & Note \\
\hline                  % inserts single horizontal line
System distance (pc)        & $132.8 \pm 2.4$     & T2012 \\
A-subsystem mass ($M_\odot$)& $2.91 \pm 0.20$     & B2007; T2012 \\
A–B semimajor axis (AU)     & $15.35 \pm 0.45$    & B2012 \\
A–B system mass ($M_\odot$) & $5.27 \pm 0.65$     & B2012 \\
B mass ($M_\odot$)          & $2.35 \pm 0.67$     & B2012 \\
\hline                                             %inserts single line
\end{tabular}
\end{table}

The KELT survey has been highly successful in discovery and analysis of systems being eclipsed by circumstellar material, including the longest period eclipsing binary \citep{Rodriguez:2016}.
%
To search for eclipses of YSOs, we cross-matched the \citet{Zari2018} catalog of young stars in the solar neighbourhood that were identified by a combination of Gaia DR2 \citep{GaiaDR2} photometry and kinematics to the KELT catalog to obtain a sample of $\sim$1450 stars with lightcurves.
%
The corresponding KELT lightcurves for each YSO target were visually inspected for any large dimming events ($>$10\%) that lasted more than a week.
%
From this analysis, we identified a $\sim$80\% deep dimming event in V773 Tau, shown in Figure~\ref{fig:lc}.
%
The eclipse is incomplete, with the first half of the eclipse occurring when V773 Tau was behind the Sun, so we only observed the egress of the eclipse that lasted $\sim$100 days.
%
Based on this discovery, we searched for the eclipse in other photometric data sets.

@@

The All Sky Automated Survey \citep[ASAS; ][]{pojmanski_all_1997, asas_2005, asas_2018} is a survey consisting of two observing stations - one in Las
Campanas, Chile and the other on Maui, Hawaii. 
%
Each observatory is equipped with two CCD cameras using V and I filters and commercial f $ = 200$ mm, D $= 100$ mm lenses, although both larger (D $= 250$ mm) and smaller (50-72 mm) lenses were used at earlier times.
%
The majority of the data are taken with a pixel scale of $\approx$ 15\arcsec{}.
%
ASAS splits the sky into 709 partially overlapping (9\degr{} $\times$ 9\degr{} fields, taking on average 150 3-minute exposures per night, leading to a variable cadence of 0.3-2 frames per night.
%
Depending on the equipment used and the mode of operation, the ASAS limiting magnitude varied between 13.5 and 15.5 mag in V, and the saturation limit was 5.5 to 7.5 mag. 
%
Precision is around 0.01-0.02 mag for bright stars and below 0.3 mag for the fainter ones. 
%
ASAS photometry is calibrated against the Tycho catalog, and its accuracy is limited to 0.05 mag for bright, non-blended stars.

 \begin{table*}
\caption{Summary of the photometric data for V773 Tau employed in this work. Surveys with a * observed the eclipse. The start and end date are in HJD-2450000 format.}              % title of Table
\label{tab:v773tau_photometry}      % is used to refer this table in the text
\centering                                      % used for centering table
\begin{tabular}{l c c c}          % centered columns (4 columns)
\hline\hline                        % inserts double horizontal lines
Survey  & Start Date & End Date & N$_{\text{points}}$ \\
\hline                  % inserts single horizontal line
ASAS*              & 2621.65 &  8879.56& 712\\
SWASP  & 3215.71 & 4542.35 &  4902\\
HATNET    &4390.97 & 4552.81 & 3402\\
PTF*     & 5543.16 & 5782.49 & 121\\
ASAS-SN   & 5946.95 & 8451.85 & 882\\
KELT*   & 7020.84 & 2986.11 & 10272\\
ASAS-SN   & 8002.90 & 9488.90  & 1630\\
TESS      & 8816.10 & 8840.87 & 999\\
\hline
\end{tabular}
\end{table*}

@@

The Transiting Exoplanet Survey Satellite \citep[TESS; ][]{2015JATIS...1a4003R} is a satellite designed to survey for transiting exoplanets among the brightest and nearest stars over most of the sky.
%
The TESS satellite orbits the Earth every 13.7 days on a highly elliptical orbit, scanning a sector of the sky spanning 24\degr $\times$ 96\degr\ for a total of two orbits, before moving on to the next sector. 
%
It captures images at a 2 second (used for guiding), 20 seconds (for 1 000 bright asteroseismology targets), 120 seconds (for 200 000 stars that are likely planet hosts) and 30 minutes (full frame image) cadences.
%
The instrument consists of 4 CCDs each with a field of view of 24\degr$\times$24\degr, with a wide band-pass filter from 600-1000 nm (similar to the $I_C$ band) and has a limiting magnitude of about 14-15 mag ($I_C$).
%
The data was extracted from the TESS archive using the {\tt eleanor} package \citep{Feinstein19} which corrected for known systematics in the cameras and telescope.

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=\columnwidth]{figures/fig3_v773tau.pdf}
    \caption{SPHERE image of V773 Tau AB and C. The axes are centred on A, and B is not visible in this image, being under the first diffraction ring of the A component.
    %
    C is shown to the lower left of AB.
    %
    North is up and East to the left.}
  \label{fig:sphere}
  \script{make_fig3_v773tau.py}
\end{figure}

>>>>

%\documentclass[referee]{aa} % for a referee version
%\documentclass[onecolumn]{aa} % for a paper on 1 column  
\documentclass{aa}

@@

\newcommand{\rsun}{$R_{\odot}$}
\newcommand{\teff}{$T_{\rm eff}$}
\newcommand{\logg}{\ensuremath{\log g}}
\newcommand{\Msun}{$M_{\odot}$}
\newcommand{\logl}{log($L/L_{\odot}$)}
\def\kms{\ifmmode{\rm km\th s^{-1}}\else km\th s$^{-1}$\fi}
\def\th{\thinspace}

\newcommand\todo[1]{\colorbox{yellow}{\textcolor{red}{#1}}}

@@

\title{Eclipse of the V773 Tau B circumbinary disc\thanks{The manuscript and processing scripts are available in a GitHub repository at \url{https://github.com/mkenworthy/V773TauBdisk}. Processed photometric data and light curves are available in electronic form at the CDS via anonymous ftp to \url{cdsarc.u-strasbg.fr} (130.79.128.5) or via \url{http://cdsweb.u-strasbg.fr/cgi-bin/qcat?J/A+A/}}}

@@

  \abstract
  % context heading (optional)
  % {} leave it empty if necessary  
   {Young multiple stellar systems can host both circumstellar and circumbinary disc composed of gas and dust, and the orientations of circumbinary discs can be sculpted by the orientation and eccentricity of the central binaries.
   %
   Studying multiple binary systems and their associated discs enables our understanding of the size and distribution of the planetary systems that subsequently form around them.}
  % aims heading (mandatory)
   {A deep ($\sim 70$\%) and extended ($\sim$150 days) eclipse was seen towards the young multiple stellar system V773 Tau in 2010.
   %
   We interpret it as being due to the passage of a circumbinary disc around the B components moving in front of the A components.
   %
 Our aim is to characterise the orientation and structure of the disc, to refine the orbits of the sub-components, and to predict when the next eclipse will occur.}
  % methods heading (mandatory)
   {We combined the photometry from several ground-based surveys, constructed a model for the light curve of the eclipse, and used high angular resolution imaging to refine the orbits of the three components of the system: A, B, and C.
   %
   A frequency analysis of the light curves, including from the TESS satellite, enabled the characterisation of the rotational periods of the Aa and Ab stars.}
  % results heading (mandatory)
   {A toy model of the circumbinary disc shows that it extends out to approximately 5 au around the B binary and has an inclination of 73\degr{} with respect to the orbital plane of AB, where the lower bound of the radius of the disc is constrained by the geometry of the AB orbit and the upper bound is set by the stability of the disc.
   %
   We identify several frequencies in the photometric data that we attribute to rotational modulation of the Aa and Ab stellar companions.
   %
   We produced the first determination of the orbit of the more distant C component around the AB system and limited its inclination to 93\degr{}.
   %
}
  % conclusions heading (optional), leave it empty if necessary 
   {The high inclination and large diameter of the disc, together with the expected inclination of the disc from theory, suggest that B is an almost equal-mass, moderately eccentric binary.
   %
   We identify the rotational periods of the Aa and Ab stars and a third frequency in the light curve that we attribute to the orbital period of the stars in the B binary.
   %
   We predict that the next eclipse will occur around 2037, during which both detailed photometric and spectroscopic monitoring will characterise the disc in greater detail.}

@@

Young multiple stellar systems are common \citep[e.g.][]{Ghez93,Duchene13}, as are gas discs in and around the stellar components \citep{Akeson19}.
%
Chaotic accretion can occur during the star formation process as a result of turbulence within the molecular cloud from which the stars form \citep{Bate2003,McKee2007}.
%
Circumstellar and circumbinary discs can form with a misalignment to the binary orbital plane \citep{Monin2007, Bate2018}.

These binaries have been shown to influence and sculpt the circumbinary discs around them, possibly reinvigorating planet formation \citep{Cabrit06,Rodriguez18}.
%
%
The torque from a binary or multiple stellar system affects the formation and evolution of gas discs \citep[e.g.][]{Nelson2000, Mayer2005,Boss2006, Fu2017} and the interaction between planets and the disc \citep{Picogna2015,Lubow2016,Martin2016}.
%
Thus, understanding how stellar multiplicity affects the formation and evolution of cs is important to explain observed exoplanet properties.

A misaligned circumbinary disc undergoes retrograde nodal precession.
%
If the binary is in a circular orbit, the precession is always around the binary angular momentum vector \citep[e.g.][]{Larwood1996}.
%
However, around an eccentric binary the precession is around the binary eccentricity vector if the initial misalignment is sufficiently high \citep{Farago2010,Aly2015}.
%
Dissipation within the disc causes it to align coplanar to the binary orbit, or polar to the binary orbit and aligned with the binary eccentricity vector \citep{Martin17,Lubow2018,Zanazzi2018}.
%
While all currently detected circumbinary planets are in coplanar orbits, around an eccentric binary polar planets may be more stable than coplanar planets \citep{Chen2020}, and terrestrial planets at least form more efficiently \citep{Childs2021}.
%
If the disc's lifetime is shorter than its alignment timescale then planets may form in misaligned orbits.

There are now many observations of circumbinary discs with a range of misalignment angles.
%
For example, KH~15D has a misalignment of about $3-15^\circ$ \citep{Chiang2004, Winn2004,Capelo2012,Poon2021}.
%
IRS~43 is misaligned by more than $60^\circ$ \citep{Brinch16}, and the circumbinary disc around 99 Her has a polar misalignment \citep{Kennedy12}.
%
HD~98800 has a misalignment of $90^\circ$, meaning it is polar aligned to the central binary orbit \citep{Kennedy19,Zuniga-Fernandez21}.
%
Of the two possible disc inclinations allowed by observations, the polar alignment was first suggested by considering the dynamics of a disc since the polar alignment timescale is short compared to the stellar age.
%
Furthermore, the size of the inner hole in the disc that is carved by the binary orbit \citep{Artymowicz1994} is in agreement with a polar alignment \citep{Franchini19}.
%
There is also an external binary companion to the circumbinary disc in this system, and its orbit is close to $34^\circ$ to the normal of the disc's angular momentum.

V773 Tau is a young multiple stellar system that has been intensively studied as described in Section~\ref{sec:v773}.
%
It contains three components, each at a distinctly different stage of young stellar evolution - the A component is an almost equal-mass binary, which in itself orbits around an almost equal-mass B component that has an edge-on disc around it, forming a hierarchical multiple system with a decades-long orbit.
%
Both these components are orbited by a third, C component that is highly embedded within a cloud of dust and is on a several-hundred-year orbit around both A and B.
%

In Section~\ref{sec:data}, we present the photometry of the V773 system from several ground-based surveys.
%
A deep extended eclipse occurs over a 200 day period, and we attribute this to a disc around the B component passing in front of the A components.
%
This disc is highly inclined with respect to the AB orbital plane, which should otherwise become coplanar within a dynamically short timescale.
%
Previous work \citep{Boden12} indicates that the B component is itself a tight, almost equal-mass binary system.
%
If the B binary is also eccentric, then the disc will experience a torque that keeps it at the inclination that we observe.
%
Time series analysis of the photometry reveals two rotational periods consistent with the stars in the A binary, and a third period of approximately 67 days is revealed in the analysis.
%
If this period is attributed to the orbital period of the B binary, we show that a moderate orbital eccentricity will keep the circumbinary disc at the observed inclination.
%
We derive the properties of the B binary and the circumbinary disc, and in Section~\ref{sec:orbitalfit} use the astrometry from the direct imaging observations to determine the expected epoch of the next eclipse of the A system.

Section~\ref{sec:variability} details our analysis of the photometric fluctuations due to rotational modulation of both Aa and Ab, and it identifies a photometric signal whose period is a plausible measure of the orbit of the BaBb binary.
%
The long and extended eclipse is modelled in Section~\ref{sec:model} as an azimuthally symmetric dusty disc that is highly inclined to the AB orbital plane.
%
Theoretical consideration of the torques from an eccentric binary on a surrounding disc are discussed in Section~\ref{sec:theory} along with the prediction for the timing of the next eclipse in Section~\ref{sec:discuss}.
%
We summarise our results and discuss future observations in Section~\ref{sec:conclusions}.

@@

\begin{figure}
\begin{center}
    \centering
    \includegraphics[width=\columnwidth]{figures/v773_system_cartoon.pdf}
    \caption{Sketch of V773 Tau system. 
    %
    We hypothesise that B is itself an equal-mass binary system with a moderately eccentric orbit.
    %
    Orbits are not to scale.}
\label{fig:cartoon}
\end{center}
\end{figure}

\begin{figure*}
\begin{center}
    \centering
    \includegraphics[width=\textwidth]{figures/fig2_full_lightcurve.pdf}
    \caption{Optical photometry of V773 Tau system.
    %
    The four different photometric surveys are represented by different colours, and each photometric series has been normalised using flux outside the main eclipse.
    %
    The inset panel shows the eclipse light curve in greater detail.
    %
    The PTF and KELT curves show different depths of the eclipse, indicating the presence of sub-micron dust that causes different amounts of optical extinction in the different pass bands of the two surveys.}
\label{fig:lc}
  \script{fig2_complete_lightcurve.py}
\end{center}
\end{figure*}

@@

V773 Tau (HD 283447, HBC 367) is a young \citep[$3\pm1$ Myr;][]{Boden07} stellar system that was identified as a young T Tauri star \citep{Rydgren76} and subsequently resolved as a visual double system \citep{Ghez93,Leinert93}.
%
Its age was determined by comparing the temperature and luminosity of the stars Aa and Ab with Pre-Main Sequence (PMS) stellar models from \citet{Montalban06}, which show excellent consistency with the component parameters from \citet{Boden07}.
%
It is located at a distance of $132.8\pm 2.3 $ pc as determined by orbital and trigonometric parallax \citep{Torres12}, in contradiction with the larger distance determined by Gaia EDR3.
%
We attribute this discrepancy to the multiple-source nature of the system that is not resolved by GAIA, and we use the distance determined by the spatially resolved A components with the VLA observations \citep{Torres12}.

The bound components of V773 Tau were initially identified as A, B, and C (see Figure~\ref{fig:cartoon}).
%
The A component was resolved by Very Long Baseline Array observations to be a binary system with $P_{AaAb}=51.1003\pm 0.0022$ days and an eccentricity of $e=0.2710\pm 0.0072$ \citep{Torres12}.
%
The A binary becomes more luminous in radio waves during the periastron passage of the A stars, which is thought to be from the interacting magnetic fields of the two stars \citep{Torres12}.

A is orbited by the B component over a period of approximately 26 years, and both A and B are orbited by a C component with an orbital period of several hundred years \citep{Duchene03}.
%
C is a heavily reddened companion that is the faintest component at a wavelength of two microns but is the brightest at $4.7\mu m$ \citep{Duchene03,Woitas03}.
%
The flux contribution from C at optical wavelengths is approximately 100 times fainter than the A and B components \citep{Duchene03}.

@@

Photometry of the B component shows a significantly greater amount of extinction compared to the A component, implying the presence of additional dust along the line of sight to the B component \citep{Torres12}.
%
The B component shows significant photometric variability of the order of 2 to 3 magnitudes in the $K$ band \citep{Boden12}, which is consistent with clouds or clumps of dust orbiting around the B component.
%
The initial fit to the spectral energy distribution (SED) suggested that the B component consisted of a single K star \citep{Duchene03}, but subsequent radial velocity monitoring and astrometry of the A binary enabled a dynamical mass determination of both the B and A components, revealing a much larger mass of $2.35 M_\odot$ for the B component \citep{Boden12}.
%
A single $2.35 M_\odot$ star would have a luminosity of $17 L_\odot$, which is inconsistent with the optical luminosity observed and the extinction derived.
%
If the B system is itself a binary, BaBb, then assuming equal-mass components of $1.5 M_\odot$ yields a much lower luminosity that is consistent with the observed SED.
%
We therefore assume that the V773 Tau AB system is a hierarchical quadruple system, with a circumbinary disc around the B component that is responsible for the significant reddening and photometric variability seen in its vicinity.

@@

% table
\begin{table*}
\caption{Orbital parameters for A and B systems. Data from \citet{Torres12} `joint solution' for AaAb and from \citet{Boden12} for A-B. We note that $\omega_A$ is defined in the RV sense for Torres and Boden, so it is necessary to add 180\degr{} to $\omega_A$ for the Torres and Boden orbits to be correctly calculated in orbitize!}              % title of Table
\label{tab:orbs}      % is used to refer this table in the text
\centering                                      % used for centering table
\begin{tabular}{l c c c c}          % centered columns (4 columns)
\hline\hline                        % inserts double horizontal lines
Orbital  & Torres 2012  & Boden 2012    & this work   &  this work \\
 Parameter & AaAb  & AB    & AB   & AB-C  \\

@@

\begin{table}
\caption{Physical parameters for V773 Tau A-B. Data from \citet{Torres12} 'joint solution' for AaAb and from \citet{Boden12} for A-B}              % title of Table
\label{tab:physparams}      % is used to refer this table in the text
\centering                                      % used for centering table
\begin{tabular}{l c c}          % centered columns (4 columns)
\hline\hline                        % inserts double horizontal lines
Parameter & Value & Note \\
\hline                  % inserts single horizontal line
System distance (pc)        & $132.8 \pm 2.4$     & T2012 \\
A-subsystem mass ($M_\odot$)& $2.91 \pm 0.20$     & B2007; T2012 \\
A–B semimajor axis (AU)     & $15.35 \pm 0.45$    & B2012 \\
A–B system mass ($M_\odot$) & $5.27 \pm 0.65$     & B2012 \\
B mass ($M_\odot$)          & $2.35 \pm 0.67$     & B2012 \\
\hline                                             %inserts single line
\end{tabular}
\end{table}

The KELT survey has been highly successful in the discovery and analysis of systems being eclipsed by circumstellar material, including the longest period eclipsing binary \citep{Rodriguez:2016}.
%
To search for eclipses of YSOs, we cross-matched the \citet{Zari2018} catalogue of young stars in the solar neighbourhood that were identified by a combination of Gaia DR2 \citep{GaiaDR2} photometry and kinematics with the KELT catalogue to obtain a sample of $\sim$1450 stars with light curves.
%
The corresponding KELT light curves for each YSO target were visually inspected for any large dimming events ($>$10\%) that lasted more than a week.
%
From this analysis, we identified an $\sim$80\% deep dimming event in V773 Tau, which is shown in Figure~\ref{fig:lc}.
%
The eclipse is incomplete, with the first half of the eclipse occurring when V773 Tau was behind the Sun, so we only observed the egress of the eclipse that lasted $\sim$100 days.
%
Based on this discovery, we searched for the eclipse in other photometric data sets.

@@

The All Sky Automated Survey \citep[ASAS; ][]{pojmanski_all_1997, asas_2005, asas_2018} is a survey consisting of two observing stations - one in Las
Campanas, Chile and the other on Maui, Hawaii. 
%
Each observatory is equipped with two CCD cameras using V and I filters and commercial f $ = 200$ mm, D $= 100$ mm lenses, although both larger (D $= 250$ mm) and smaller (50-72 mm) lenses were used at earlier times.
%
The majority of the data were taken with a pixel scale of $\approx$ 15\arcsec{}.
%
ASAS splits the sky into 709 partially overlapping (9\degr{} $\times$ 9\degr{} fields, taking on average 150 3-minute exposures per night, leading to a variable cadence of 0.3-2 frames per night.
%
Depending on the equipment used and the mode of operation, the ASAS limiting magnitude varied between 13.5 and 15.5 mag in V, and the saturation limit was 5.5 to 7.5 mag. 
%
Precision is around 0.01-0.02 mag for bright stars and below 0.3 mag for the fainter ones. 
%
ASAS photometry is calibrated against the Tycho catalogue, and its accuracy is limited to 0.05 mag for bright, non-blended stars.

 \begin{table*}
\caption{Summary of the photometric data for V773 Tau employed in this work. Surveys with an asterisk observed the eclipse. The start and end date are in HJD-2450000 format.}              % title of Table
\label{tab:v773tau_photometry}      % is used to refer this table in the text
\centering                                      % used for centering table
\begin{tabular}{l c c c}          % centered columns (4 columns)
\hline\hline                        % inserts double horizontal lines
Survey  & Start Date & End Date & N$_{\text{points}}$ \\
\hline                  % inserts single horizontal line
ASAS*              & 2621.65 &  8879.56& 712\\
SWASP  & 3215.71 & 4542.35 &  4902\\
HATNET    &4390.97 & 4552.81 & 3402\\
PTF*     & 5543.16 & 5782.49 & 121\\
ASAS-SN   & 5946.95 & 8451.85 & 882\\
KELT*   & 7020.84 & 2986.11 & 10272\\
ASAS-SN   & 8002.90 & 9488.90  & 1630\\
TESS      & 8816.10 & 8840.87 & 999\\
\hline
\end{tabular}
\end{table*}

@@

The Transiting Exoplanet Survey Satellite \citep[TESS; ][]{2015JATIS...1a4003R} is a satellite designed to survey for transiting exoplanets among the brightest and nearest stars over most of the sky.
%
The TESS satellite orbits the Earth every 13.7 days on a highly elliptical orbit, scanning a sector of the sky spanning 24\degr $\times$ 96\degr\ for a total of two orbits, before moving on to the next sector. 
%
It captures images at two-second (used for guiding), 20-second (for 1 000 bright asteroseismology targets), 120-second (for 200 000 stars that are likely planet hosts), and 30-minute (full frame image) cadences.
%
The instrument consists of four CCDs each with a field of view of 24\degr$\times$24\degr, a wide band-pass filter from 600-1000 nm (similar to the $I_C$ band), and a limiting magnitude of about 14-15 mag ($I_C$).
%
The data were extracted from the TESS archive using the {\tt eleanor} package \citep{Feinstein19}, which corrected for known systematics in the cameras and telescope.

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=\columnwidth]{figures/fig3_v773tau.pdf}
    \caption{SPHERE image of V773 Tau AB and C. The axes are centred on A, and B is not visible in this image as it is under the first diffraction ring of the A component.
    %
    C is shown to the lower left of AB.
    %
    North is up and east to the left.}
    \label{fig:sphere}
  \script{make_fig3_v773tau.py}
\end{figure}
